Prestige bias in cultural evolutionary dynamics

### 2023-02-07 ms/ms.tex
revise abstract

\begin{abstract}
A common bias in cultural transmission is to copy whoever appears more successful. This success bias only depends on the performance of the role-model.
Because success may be difficult to estimate, it has been suggested that individuals may indirectly estimate success by using prestige as a proxy for success. Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied from that role-model.
We analyze the effect of prestige on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduce the computational complexity of simulations. We also find approximations to the fixation probability and the fixation time of an invading cultural trait in different environments. 
We show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
Influence bias also accelerates the evolutionary dynamics, as can be expected in a \emph{rich-getting-richer} process.
Our model describes and analyses cultural transmission, especially in human societies where social media is popular.

\end{abstract}

>>>>

\begin{abstract}
A common bias in cultural transmission is success bias, where more successful individuals are more likely to be copied.
Because success may be difficult to estimate, individuals may indirectly estimate success by using prestige as a proxy for success. Here, we model prestige bias as a combination of indirect success bias and influence bias, the latter meaning that the choice of a role-model depends on the number of individuals that have already copied from that role-model.
We analyze the effect of prestige on cultural evolutionary dynamics using mathematical analysis and stochastic simulations.
We find analytic approximations to the stochastic role-model choice process, which facilitate further mathematical analysis and reduce the computational complexity of simulations. We also find approximations to the fixation probability and the fixation time of an invading cultural trait in different environments. 
We show that indirect success bias effectively plays the role of natural selection, whereas influence bias effectively plays the role of genetic drift.	
Influence bias also accelerates the evolutionary dynamics, as can be expected in a rich-getting-richer process.
Our study extends the literature that describes and analyses cultural transmission,
especially in human societies where social media is popular and thus influence bias may be expected.
\end{abstract}
